Investigating the Impact of Macroeconomic Indicators on the FTSE 250 Index Using Statistical and Machine Learning Methods

### 2024-08-24 tex/paper.tex
intro revised

on the FTSE 250 Index Using Statistical \& Machine Learning Methods}
\author{Mateen Khan}
\date{\today}

@@

The stock market is a significant component of the financial system and 
plays a crucial role in the broader economy. Consequently, economic policy 
makers take the stock market into account when making fiscal policy 
decisions using a combination of quantitative and qualitative methods. 
These methods such as econometric modelling and forecasting, and empirical 
analysis allow them to understand the short-term and long-term effects of 
macroeconomic indicators such as taxation rates, interest rates and exchange rates,
on the wider economy through the stock market.

Macroeconomic indicators can be effectively used in machine learning 
methods to forecast stock prices by serving as input features that capture 
the economic environment’s influence on market behaviour. By carefully 
selecting the most relevant indicators and preprocessing data, 
as well as choosing appropriate models, machine learning can enhance the accuracy of stock price forecasts (\citeboth{Sarma2023,Prasad2023}).

@@

In particular, the objectives of this study are to address how specific macroeconomic indicators influence stock market prices in a developed economy, and whether machine learning models can substitute traditional econometric models in predicting stock market prices. It aims to:
\begin{enumerate}
    \item examine the short-term and long-term effects of macroeconomic indicators on the price of the FTSE250
    \item investigate whether machine learning techniques can provide accurate short-term and long-term forecasts of the price of the FTSE250 when using a small, coarse-grain dataset.
\end{enumerate}

>>>>

on the FTSE 250 Index Using Statistical and Machine Learning Methods}
\author{Mateen Khan}
\date{\today}

@@

The stock market is a significant component of the financial system and 
plays a crucial role in the broader economy. Consequently, economic policy 
makers take the stock market into account when making fiscal policy 
decisions using a combination of quantitative and qualitative methods. 
These methods such as econometric modelling and forecasting, and empirical 
analysis allow them to understand the short-term and long-term effects of 
macroeconomic indicators
on the wider economy through the stock market (\citeboth{DemirgucKunt1996}).

Macroeconomic indicators can be effectively used in machine learning 
methods to forecast stock prices by serving as input features that capture 
the economic environment’s influence on market behaviour. By carefully 
selecting the most relevant indicators and preprocessing data, 
as well as choosing appropriate models, machine learning can enhance the accuracy of stock price forecasts (\citeboth{Prasad2023}).

@@

In particular, the objectives of this study are to address how specific macroeconomic indicators influence stock market prices in a developed economy, and whether machine learning models can substitute traditional econometric models in predicting stock market prices. It aims to:
\begin{enumerate}
    \item examine the short-term and long-term effects of macroeconomic indicators on the price of the FTSE250
    \item investigate whether machine learning techniques can provide accurate short-term and long-term forecasts of the price of the FTSE250 when using a small dataset.
\end{enumerate}
